### 2017-08-08 doc/manual/version3/inputParameters.tex
Updated user manual. Made sure adjoint inputs are initialized.

>>>>

\param{nMaxAdjoint}
{integer}
{0}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}}
{Sensitivity of Fourier harmonics of $\bm{B}$ will be computed for $\abs{n} \leq $ \texttt{nMaxAdjoint}.}

\param{mMaxAdjoint}
{integer}
{0}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}}
{Sensitivity of Fourier harmonics of $\bm{B}$ will be computed for $m \leq$ \texttt{mMaxAdjoint}.}
